




\section{Introduction}
\label{chap:intro}

One of the main objectives of the business cycle literature prevalent in modern macro economics is to characterize ways to stabilise economies subject to these cycles. 
The need for stabilization is usually argued by considering the negative effects of declines in output, consumption and employment and the resulting effects on welfare during recessions. Still, some have argued that the welfare costs arising from cycles are so marginal that policy intuitions are better of focusing on long run, supply side policy. This among others the argument of Nobel laureate Robert Lucas Jr. (\citet{lucas2003macroeconomic}). Other researchers find more significant efficiency losses arsing from business cycles (see \citet{gali2007markups}, \citet{tella2003macroeconomics} etc.). 


In brief, the welfare losses can be decomposed into three channels: A consumption channel, an uncertainty channel, and an effort/well-being related channel. The first channel captures the direct welfare loss which inevitably occurs during a recession when production, income and thus consumption declines. The second channel refers to the fact that consumers are generally risk averse, and thus incur welfare losses when income streams are volatile. Technically, the first channel arises from first-order effects on utility and the second channel arises from second-order effects. The third channel relates to subjective well-being, the most prominent one being that of the negative psychological consequences of unemployment spells (\citet{wolfers2003business}).

Let us for a minute (or the rest of this thesis) assume that the above channels add up to such large welfare losses that stabilization is needed. The most studied instruments in the literature in dealing with economic fluctuations are monetary and government policy. Both appear in discretionary versions, but also adhere to certain rules. For monetary policy, the Taylor rule is well known. For government policy, various rules of law act as automatic stabilizers to the economy. The most well-known examples include unemployment benefits, progressive income taxation, corporate taxes etc. Unemployment benefits reduce fluctuations by lessening the income change that occur when people move in and out of employment. Similarly, progressive taxation reduce income fluctuations since disposable income is a convex function of taxable income under such a system.  Stabilizing income in turn stabilizes consumer demand thus reducing economic fluctuations. This type of stabilizers generally imply that the government's budget balance is procyclical, other things equal.   

The main subject of this thesis is the valuation of these automatic stabilizers in reducing business cycle fluctuations. The main novelty is that the frame of analysis is a fully fleshed out heterogeneous agent New Keynesian (HANK) model. Using heterogeneous agent (HA) models as opposed to representative agent (RA) has importance applications for the impact of automatic stabilizers. HA models enhance models with a number of features, but with respect to analyzing automatic stabilizers the most important feature is the presence of endogenous hand-to-mouth (HtM) consumers. Recall that HtM consumers denote consumers that simply consume all their income and thus holds no savings. This kind of behavior tend to occur for households that credit constrained. Since the average household is not credit constrained HtM behavior does not appear in true RA models. A wide class of models contain a "standard" Ricardian household and a HtM household to mimic this credit constrained behavior. Typically, the HtM household is modelled as a consumer that simply "eats" his/hers entire income each period. 

The importance of this in relation automatic stabilizers is straightforward. During a recession more agents become unemployed. This implies large drops in income, and agents that before the recession had small amounts of savings might become credit constrained now and thus essentially move in HtM territory. Since HtM agents has large marginal propensities to consume...
% Ricardian Equiv. 





\subsection{Existing Literature}
\subsubsection{Automatic Stabilizers}

\citet{mckay2016role}
\citet{mckay2016optimal}




\subsubsection{HANK Models}
The emergence of heterogeneous agent New Keynesian models is relatively recent, which in turn owes to too reasons. Firstly, the textbook 3 equation NK model is itself relatively young, primarily owing to \citet{goodfriend1997new}, \citet{clarida1999science}, \citet{woodford2003interest}. This model was conceived by merging the real business cycle models of \citet{kydland1982time} with nominal rigidities and market power of firms from the Keynes paradigm. Following the initial appearance of the NK models several medium/large scale versions were later constructed, see \citet{smets2003estimated}, \citet{smets2007shocks}. These usually extended the canonical NK model by have capital accumulation, investment adjustment costs, variable capital utilization, sticky wges etc. 

In recent year a strand of the literature has emerged that combines NK models with heterogeneous agent models al a \citet{bewley1986stationary}, \citet{aiyagari1994uninsured}, \citet{krusell1998income}. A notable feature of these heterogeneous agent models is that they typically feature incomplete markets. For households this imply that there is not a complete set of Arrow-Debreu state contingent claims to fully insure against earnings risk. This in turn generates precautionary savings motives. Following \citet{kaplan2018monetary} the merge of these different kind of models have been dubbed HANK models. The majority of work on these models have occurred within the last 10 years, which among other reasons is due to increased computational power. This is important since solving HANK models involve solving a Dynamic Programming problem which may contain several state variables and idiosyncratic shocks. \\
 
HANK models have already been applied to a wide amount of central macroeconomic questions such as the effects of monetary policy (\citet{kaplan2018monetary},  \citet{auclert2020micro})

Auclert etc: 
\citet{auclert2018inequality} % Inequality and aggregate demand
\citet{auclert2019using} % SHADE 
\citet{auclert2018intertemporal} % The intertemporal keynesian cross
\citet{auclert2020micro} % Micro Jumps, Macro Humps: monetary policy and business cycles in an estimated HANK model

%Kaplan: 
%\citet{kaplan2018monetary} % Monetary policy according to HANK

Ravn: 
\citet{ravn2016macroeconomic} % Macroeconomic fluctuations with HANK \& SAM: An analytical approach


 
 